---
title: "First Draft of Code"
output: html_document
data: 4/11-2020
authors: Rasmus Vesti Hansen & Emil Buus Thomsen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This will be the first draft for our final project. In this file we will try to clean the data gathered on abortions, average income and population based on municipalities in Denmark. 
The sources for our data are the following: 
Average income in Danish municipalities: https://www.statistikbanken.dk/INDKP101 
Abortions in Danish municipalities: https://www.esundhed.dk/home/registre/register%20over%20provokerede%20aborter 
Population in Danish municipalities: http://www.noegletal.dk/ (Here we selected all municipalities and searched for population from 1995-2020)

After having found the correct data we use OpenRefine to clean the Data into .csv files so it is easy to load into R. 
In OpenRefine we use the transform tool to clean the data by replacing the "." with nothing ("") so the numbers will be correct. After this we use value.toNumber() to make the columns numeric. 

After we made a shared repository on GitHub so it would be easy for both us to access the data and scripts. 

Then we are defining our data into Data Frames
```{r}
AverageIncome <- read.csv("Rigtig_Data_CSV/Income_male_and_female.csv")
AbortionsData <- read.csv("Rigtig_Data_CSV/Abortions_DK_1995_2018.csv")
PopulationMun <- read.csv("Rigtig_Data_CSV/Population_pr_municipalities.csv")

options(max.print = 99999)


```

AverageIncome

AbortionsData 

PopulationMun


The plan now is for AbortionsData to calculate through PopulationCom the abortions pr. capita instead of the number of abortions in the commune as that would give a more representative view on the data. Regarding this it is also worth considering whether to have the population in municipalities of female or both genders.  
In the data we also have a problem as the dataset on the number of abortions have a "<5" value, which is being classified as a character and does not count as a specific. What should we do? 

After this we want to visualize the data on abortions pr. capita in correalation with the AverageIncome and see if there is a connection. 
